---
title: "Lab 6"
author: "Hershel Mehta"
date: "7/18/2017"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ISLR)
library(leaps)
```

# 6.5.3 Choosing Among Models Using the Validation Set Approach and Cross-Validation

```{r}
set.seed(1)

train <- sample_frac(Hitters, 0.5)
test <- setdiff(Hitters, train)
```

First, create a dataframe with one column, "p" = the size of the model (i.e., the number of predictors used in best subset)

```{r}
best_subset_coef <- function(x, p_) {
  train_data <- as_tibble(x)
  
  best_subset_model <- leaps::regsubsets(Salary ~ ., train_data, nvmax = 19)
  
  best_subset_coef <- coef(best_subset_model, p_)
  
  tail(names(best_subset_coef), n = -1)
}
```

```{r}
best_subset_lm_fit <- function(x, var_names) {
  train_data <- as_tibble(x) 
  
  lm(Salary ~ ., data = train_data %>% select(Salary, one_of(var_names)) )
}
```

We write a function that takes the number of predictors "p_" for best subset and number of folds "k_", and does the following:

* Splits the data using k-Fold Cross-Validation (using `resamplr::crossv_kfold`)
* Creates two new columns containing:
    + the best model of degree "n_" fit to the training split
    + The "RMSE" of the model tested on the testing split
* Returns the mean "RMSE" across all folds

```{r}
p_ <- 19
k_ <- 10

best_subset <- 
  Hitters %>% 
  resamplr::crossv_kfold(k_) %>% 
  mutate(
    var_names = map2(train, p_, best_subset_coef),
    model = map2(train, var_names, best_subset_lm_fit),
    rmse = map2_dbl(model, test, modelr::rmse)
  )

best_subset$var_names
```


```{r}
best_subset_kfold <- function(p_, k_) {
  best_subset <- 
    Hitters %>% 
    resamplr::crossv_kfold(k_) %>% 
    mutate(
      var_names = map2(train, p_, best_subset_coef),
      model = map2(train, var_names, best_subset_lm_fit),
      rmse = map2_dbl(model, test, modelr::rmse)
    )

  mean(best_subset$rmse)
}
```

We call the function on each of the desired polynomial degrees, to obtain the mean "RMSE" using k-Fold Cross-Validation on degree "n" with "k" folds.

```{r}
num_variables <- tibble(
  p = 1:19
)
```

```{r}
num_variables %>% 
  mutate(
    mean_rmse = map2_dbl(p, 10, best_subset_kfold)
  )
```

