---
title: "ISLR-Chapter-4-lab"
author: "Christopher Oh"
date: 2017-07-12
output:
  html_document:
    toc: true
    toc_depth: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 400, out.width = "100%")
```

```{r}
#Libraries to be used.
library(tidyverse)
library(ISLR)
```

# Chapter 4 Lab: Logistic Regression, LDA, QDA, and KNN

# The Stock Market Data


```{r}
names(Smarket)
dim(Smarket)
summary(Smarket)
pairs(Smarket)
cor(Smarket)
cor(Smarket[,-9])
View(Smarket)
Smarket %>% 
  mutate(index = row_number()) %>% 
  ggplot(aes(index, Volume)) +
  geom_line()

```

# Logistic Regression

Wrong way

```{r}
glm.fits=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Smarket,family=binomial)
summary(glm.fits)
coef(glm.fits)
summary(glm.fits)$coef
summary(glm.fits)$coef[,4]
glm.probs=predict(glm.fits,type="response")
glm.probs[1:10]
contrasts(Direction)
glm.pred=rep("Down",1250)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction)
(507+145)/1250
mean(glm.pred==Direction)
```

Split into training / test

```{r}
train=(Year<2005)
Smarket.2005=Smarket[!train,]
dim(Smarket.2005)
Direction.2005=Direction[!train]
glm.fits=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Smarket,family=binomial,subset=train)
glm.probs=predict(glm.fits,Smarket.2005,type="response")
glm.pred=rep("Down",252)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction.2005)
mean(glm.pred==Direction.2005)
mean(glm.pred!=Direction.2005)
glm.fits=glm(Direction~Lag1+Lag2,data=Smarket,family=binomial,subset=train)
glm.probs=predict(glm.fits,Smarket.2005,type="response")
glm.pred=rep("Down",252)
glm.pred[glm.probs>.5]="Up"
table(glm.pred,Direction.2005)
mean(glm.pred==Direction.2005)
106/(106+76)
predict(glm.fits,newdata=data.frame(Lag1=c(1.2,1.5),Lag2=c(1.1,-0.8)),type="response")
```

Revised

```{r}
smarket <- as.tibble(Smarket)
```

Separate the training / test set

```{r}
train <-
  smarket %>%
  filter(Year < 2005)
test <-
  smarket %>% 
  filter(Year >= 2005)
```

Logistic regression model on the training set

```{r}
glm_fit <- 
  glm(
    Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume,
    data = train,
    family = binomial
  )
```

Add prediction to the test set

```{r}
test <-
  test %>%
  mutate(
    pred = predict(glm_fit, newdata = test, type = "response"),
    pred_dir = ifelse(pred > .5, "Up", "Down")
  )
```

Calculate the error on the test set

```{r}
test %>%
  select(Direction, pred_dir) %>% 
  mutate(err = ifelse(Direction != pred_dir, 1, 0)) %>% 
  summarize(mean(err))
```

# Linear Discriminant Analysis

```{r}
library(MASS)
lda.fit=lda(Direction~Lag1+Lag2,data=Smarket,subset=train)
lda.fit
plot(lda.fit)
lda.pred=predict(lda.fit, Smarket.2005)
names(lda.pred)
lda.class=lda.pred$class
table(lda.class,Direction.2005)
mean(lda.class==Direction.2005)
sum(lda.pred$posterior[,1]>=.5)
sum(lda.pred$posterior[,1]<.5)
lda.pred$posterior[1:20,1]
lda.class[1:20]
sum(lda.pred$posterior[,1]>.9)
```

Revised

```{r}
lda_fit <- lda(Direction ~ Lag1 + Lag2, data = train)
lda_pred <- predict(lda_fit, test)
test %>%
  mutate(lda_pred = lda_pred$class) %>% 
  summarize(accuracy = mean(lda_pred == Direction))
test %>%
  mutate(lda_post = lda_pred$posterior[, 1])
sum(lda_pred$posterior[, 1] > .9)
```


# Quadratic Discriminant Analysis

qda.fit=qda(Direction~Lag1+Lag2,data=Smarket,subset=train)
qda.fit
qda.class=predict(qda.fit,Smarket.2005)$class
table(qda.class,Direction.2005)
mean(qda.class==Direction.2005)

# K-Nearest Neighbors

library(class)
train.X=cbind(Lag1,Lag2)[train,]
test.X=cbind(Lag1,Lag2)[!train,]
train.Direction=Direction[train]
set.seed(1)
knn.pred=knn(train.X,test.X,train.Direction,k=1)
table(knn.pred,Direction.2005)
(83+43)/252
knn.pred=knn(train.X,test.X,train.Direction,k=3)
table(knn.pred,Direction.2005)
mean(knn.pred==Direction.2005)

# An Application to Caravan Insurance Data

dim(Caravan)
attach(Caravan)
summary(Purchase)
348/5822
standardized.X=scale(Caravan[,-86])
var(Caravan[,1])
var(Caravan[,2])
var(standardized.X[,1])
var(standardized.X[,2])
test=1:1000
train.X=standardized.X[-test,]
test.X=standardized.X[test,]
train.Y=Purchase[-test]
test.Y=Purchase[test]
set.seed(1)
knn.pred=knn(train.X,test.X,train.Y,k=1)
mean(test.Y!=knn.pred)
mean(test.Y!="No")
table(knn.pred,test.Y)
9/(68+9)
knn.pred=knn(train.X,test.X,train.Y,k=3)
table(knn.pred,test.Y)
5/26
knn.pred=knn(train.X,test.X,train.Y,k=5)
table(knn.pred,test.Y)
4/15
glm.fits=glm(Purchase~.,data=Caravan,family=binomial,subset=-test)
glm.probs=predict(glm.fits,Caravan[test,],type="response")
glm.pred=rep("No",1000)
glm.pred[glm.probs>.5]="Yes"
table(glm.pred,test.Y)
glm.pred=rep("No",1000)
glm.pred[glm.probs>.25]="Yes"
table(glm.pred,test.Y)
11/(22+11)


